Direction-aware functional class scoring enrichment analysis of Infinium DNA methylation data

### 2024-02-17 manuscript/manuscript.Rmd
dockerhub link
affiliations

3. Deakin University, School of Exercise and Nutrition, Burwood, Australia.

@@

Code to generate the results shown here are included in a GitHub repository (https://github.com/markziemann/gmea/).
To enable reproduction of the findings, a docker image is made available at DockerHub
(https://hub.docker.com/repository/docker/mziemann/gmea/general).
A reproducible example workflow report is hosted on our website (https://ziemann-lab.net/public/gmea/example_workflow.html).

>>>>

3. Deakin University, School of Exercise and Nutrition Sciences, Institute for Physical Activity and Nutrition, Geelong, Australia.

@@

Code to generate the results shown here are included in a GitHub repository (https://github.com/markziemann/gmea/).
To enable reproduction of the findings, a docker image is made available at DockerHub
(https://hub.docker.com/repository/docker/mziemann/gmea).
A reproducible example workflow report is hosted on our website (https://ziemann-lab.net/public/gmea/example_workflow.html).
